---
title: "Impact of car attributes on milage"
author: "Alexander Pyle, <apyle@github.com>"
date: "October 9, 2016"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

## Overview

The Moter Trend data from the `mtcars` data set contains key information that 
can be used to answer questions about transmissions and milage. For instance, we
can find answers to the questions:

- "Is an automatic or manual transmission better for MPG"
- "How different is the MPG between automatic manual transmission?"

The field `mtcars$am` contains the type of transmission, 0 is for automatic, and 
1 is for manual transmissions.
```{r overview, echo=TRUE}
### echo s.b. FALSE for production, is TRUE for development

# load required libraries
library(data.table)
library(dplyr)
library(ggplot2)
library(xtable)

# get our data
data(mtcars)
myCars <- mutate (mtcars, transF = factor(am, labels = c("Automatic", "Manual")))
#rownames(myCars) <- rownames(mtcars)

# create a quick plot of the data
gp <- ggplot(myCars, aes(x=transF, y=mpg, fill=transF))
gp <- gp + geom_boxplot()
gp <- gp + labs(title = "Figure 0.1: Spread of milage by transmission",
                x = "Transmission", y = "Miles per Gallon")
gp <- gp + guides(fill = guide_legend(title = "Transmission Type"))
gp

myCars

#gp <- ggplot(myCars, aes(x=am, y=mpg))
#gp <- gp + geom_smooth(method = "lm", color = "black")
#gp <- geom_point(size = 7, color = "black", alpha = 0.5)
#gp <- geom_point(size = 5, color = "blue", alpha = 0.5)
#gp <- gp + labs(title = "Figure 0.2: Spread of milage by transmission",
#                x = "Transmission", y = "Miles per Gallon")
#gp

plot(mtcars$am, mtcars$mpg)

# variables used in the text and code, reinitiallized in the next chunk. Set here for use in text
lambda <- 0.2   # given by assignment
samples <- 40   # number of samples to use for the mean
simulations <- 1000     # number of simulations to run
popmean <- 1/lambda     # theoretical mean of the population
popvariance <- (1/lambda)^2 / samples # theoretical variance of the population

```

Thesis statement goes here

## Exploration



```{r exploration}

```



## Analysis



```{r analysis}

```



## Conclusion

Summary of what we discovered.

## Appendix

R Markdown source code for this analysis can be found at https://github.com/apyle/RegModels_PeerAssessment. 
This analysis was run with the following configuration. 

```{r warning=FALSE}
library(devtools)
devtools::session_info() # display environment the script was create and run in.

```

